%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

% inlined bib file
\usepackage{filecontents}

%-------------------------------------------------------------------------------
\begin{filecontents}{\jobname.bib}
%-------------------------------------------------------------------------------
@Book{arpachiDusseau18:osbook,
  author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
  title =        {Operating Systems: Three Easy Pieces},
  publisher =    {Arpaci-Dusseau Books, LLC},
  year =         2015,
  edition =      {1.00},
  note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
}
@InProceedings{waldspurger02,
  author =       {Waldspurger, Carl A.},
  title =        {Memory resource management in {VMware ESX} server},
  booktitle =    {USENIX Symposium on Operating System Design and
                  Implementation (OSDI)},
  year =         2002,
  pages =        {181--194},
  note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
@inproceedings {SLMDB,
author = {Olzhas Kaiyrakhmet and Songyi Lee and Beomseok Nam and Sam H. Noh and Young-ri Choi},
title = {SLM-DB: Single-Level Key-Value Store with Persistent Memory},
booktitle = {17th {USENIX} Conference on File and Storage Technologies ({FAST} 19)},
year = {2019},
isbn = {978-1-939133-09-0},
address = {Boston, MA},
pages = {191--205},
url = {https://www.usenix.org/conference/fast19/presentation/kaiyrakhmet},
publisher = {{USENIX} Association},
month = feb,
}
@article{PCM,
  author    = {H.{-}S. Philip Wong and
               Simone Raoux and
               SangBum Kim and
               Jiale Liang and
               John P. Reifenberg and
               Bipin Rajendran and
               Mehdi Asheghi and
               Kenneth E. Goodson},
  title     = {Phase Change Memory},
  journal   = {Proceedings of the {IEEE}},
  volume    = {98},
  number    = {12},
  pages     = {2201--2227},
  year      = {2010},
  url       = {https://doi.org/10.1109/JPROC.2010.2070050},
  doi       = {10.1109/JPROC.2010.2070050},
  timestamp = {Thu, 08 Jun 2017 09:04:07 +0200},
  biburl    = {https://dblp.org/rec/journals/pieee/WongRKLRRAG10.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}
@misc{3DXPoint,
  author = {Intel},
  title = {Intel and micron produce breakthrough memory technology.},
  howpublished = {
  \url{https://newsroom.intel.com/news-releases/intel-and-micronproduce-
breakthrough-memory-technology/}
  }
}
@misc{NVMRocks,
  author = {NVMRocks},
  title = {RocksDB on Non-Volatile Memory Systems},
  howpublished = {
  \url{http://istc-bigdata.org/index.php/nvmrocks-rocksdb-on-non-volatilememory-systems/}
  }
}
@inproceedings{DBLP:conf/usenix/XiaJXS17,
  author    = {Fei Xia and
               Dejun Jiang and
               Jin Xiong and
               Ninghui Sun},
  editor    = {Dilma Da Silva and
               Bryan Ford},
  title     = {HiKV: {A} Hybrid Index Key-Value Store for {DRAM-NVM} Memory Systems},
  booktitle = {2017 {USENIX} Annual Technical Conference, {USENIX} {ATC} 2017, Santa
               Clara, CA, USA, July 12-14, 2017},
  pages     = {349--362},
  publisher = {{USENIX} Association},
  year      = {2017},
  url       = {https://www.usenix.org/conference/atc17/technical-sessions/presentation/xia},
  timestamp = {Mon, 16 Jul 2018 15:47:23 +0200},
  biburl    = {https://dblp.org/rec/conf/usenix/XiaJXS17.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}
@inproceedings{DBLP:conf/fast/LeeLSNN17,
  author    = {Se Kwon Lee and
               K. Hyun Lim and
               Hyunsub Song and
               Beomseok Nam and
               Sam H. Noh},
  editor    = {Geoff Kuenning and
               Carl A. Waldspurger},
  title     = {{WORT:} Write Optimal Radix Tree for Persistent Memory Storage Systems},
  booktitle = {15th {USENIX} Conference on File and Storage Technologies, {FAST}
               2017, Santa Clara, CA, USA, February 27 - March 2, 2017},
  pages     = {257--270},
  publisher = {{USENIX} Association},
  year      = {2017},
  url       = {https://www.usenix.org/conference/fast17/technical-sessions/presentation/lee-se-kwon},
  timestamp = {Tue, 28 Mar 2017 15:26:05 +0200},
  biburl    = {https://dblp.org/rec/conf/fast/LeeLSNN17.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}
@inproceedings{DBLP:conf/usenix/KannanBGAA18,
  author    = {Sudarsun Kannan and
               Nitish Bhat and
               Ada Gavrilovska and
               Andrea C. Arpaci{-}Dusseau and
               Remzi H. Arpaci{-}Dusseau},
  editor    = {Haryadi S. Gunawi and
               Benjamin Reed},
  title     = {Redesigning {LSMs for Nonvolatile Memory} with {NoveLSM}},
  booktitle = {2018 {USENIX} Annual Technical Conference, {USENIX} {ATC} 2018, Boston,
               MA, USA, July 11-13, 2018},
  pages     = {993--1005},
  publisher = {{USENIX} Association},
  year      = {2018},
  url       = {https://www.usenix.org/conference/atc18/presentation/kannan},
  timestamp = {Mon, 16 Jul 2018 15:48:02 +0200},
  biburl    = {https://dblp.org/rec/conf/usenix/KannanBGAA18.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}
\end{filecontents}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Formatting Submissions for a USENIX Conference:\\
  An (Incomplete) Example}

%for single author (just remove % characters)
\author{
{\rm Your N.\ Here}\\
Your Institution
\and
{\rm Second Name}\\
Second Institution
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

%-------------------------------------------------------------------------------
\input{Abstract}
%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------
\input{Introduction}
%-------------------------------------------------------------------------------
\input{BackgroundAndMotivation}

%-------------------------------------------------------------------------------
\section{Footnotes, Verbatim, and Citations}
%-------------------------------------------------------------------------------

Footnotes should be places after punctuation characters, without any
spaces between said characters and footnotes, like so.%
\footnote{Remember that USENIX format stopped using endnotes and is
  now using regular footnotes.} And some embedded literal code may
look as follows.

\begin{verbatim}
int main(int argc, char *argv[]) 
{
    return 0;
}
\end{verbatim}

Now we're going to cite somebody. Watch for the cite tag. Here it
comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
about resource management in the ESX hypervisor~\cite{waldspurger02,SLMDB}.

The tilde character (\~{}) in the tex source means a non-breaking
space. This way, your reference will always be attached to the word
that preceded it, instead of going to the next line.

And the 'cite' package sorts your citations by their numerical order
of the corresponding references at the end of the paper, ridding you
from the need to notice that, e.g, ``Waldspurger'' appears after
``Arpachi-Dusseau'' when sorting references
alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}. 

It'd be nice and thoughtful of you to include a suitable link in each
and every bibtex entry that you use in your submission, to allow
reviewers (and other readers) to easily get to the cited work, as is
done in all entries found in the References section of this document.

Now we're going take a look at Section~\ref{sec:figs}, but not before
observing that refs to sections and citations and such are colored and
clickable in the PDF because of the packages we've included.

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}
\label{sec:figs}
%-------------------------------------------------------------------------------


%---------------------------
\begin{figure}
\begin{center}
\begin{tikzpicture}
  \draw[thin,gray!40] (-2,-2) grid (2,2);
  \draw[<->] (-2,0)--(2,0) node[right]{$x$};
  \draw[<->] (0,-2)--(0,2) node[above]{$y$};
  \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
        node[anchor=south west]{$\boldsymbol{u}$};
  \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
        node[anchor=north east]{$\boldsymbol{-u}$};
\end{tikzpicture}
\end{center}
\caption{\label{fig:vectors} Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. }
\end{figure}
%% %---------------------------


Here's a typical reference to a floating figure:
Figure~\ref{fig:vectors}. Floats should usually be placed where latex
wants then. Figure\ref{fig:vectors} is centered, and has a caption
that instructs you to make sure that the size of the text within the
figures that you use is as big as (or bigger than) the size of the
text in the caption of the figures. Please do. Really.

In our case, we've explicitly drawn the figure inlined in latex, to
allow this tex file to cleanly compile. But usually, your figures will
reside in some file.pdf, and you'd include them in your document
with, say, \textbackslash{}includegraphics.

Lists are sometimes quite handy. If you want to itemize things, feel
free:

\begin{description}
  
\item[fread] a function that reads from a \texttt{stream} into the
  array \texttt{ptr} at most \texttt{nobj} objects of size
  \texttt{size}, returning returns the number of objects read.

\item[Fred] a person's name, e.g., there once was a dude named Fred
  who separated usenix.sty from this file to allow for easy
  inclusion.
\end{description}

\noindent
The noindent at the start of this paragraph in its tex version makes
it clear that it's a continuation of the preceding paragraph, as
opposed to a new paragraph in its own right.


\subsection{LaTeX-ing Your TeX File}
%-----------------------------------

People often use \texttt{pdflatex} these days for creating pdf-s from
tex files via the shell. And \texttt{bibtex}, of course. Works for us.
\input{Evaluation}
\input{RelatedWork}
\input{Conclusion}
%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

The USENIX latex style is old and very tired, which is why
there's no \textbackslash{}acks command for you to use when
acknowledging. Sorry.

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

USENIX program committees give extra points to submissions that are
backed by artifacts that are publicly available. If you made your code
or data available, it's worth mentioning this fact in a dedicated
section.

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{\jobname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks
